The Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2014-01-23 papers/pair-correlation/paper.tex
More pair plot tweaks Tested on paho-arch. Took 1:04.43.

\newcommand\paircaption[1]{ The pair distribution function near a hard
  wall, with a packing fraction of #1, with $\rr_1$ in contact with
  the hard wall.  On the left is a 2D plot of $g^{(2)}(\rr_1,\rr_2)$
  as $\rr_2$ varies.  The top half of this figure shows the result of
  Monte Carlo simulation, while the bottom half shows the result of
  the appproximation developed in this work.  On the right is a plot
  of $g^{(2)}(\rr_1,\rr_2)$ on the path illustrated in the figure to
  the left.  This plot compares the Monte Carlo results (black) with
  those of this work (color?), Sokolowski and Fischer
  (color?)~\cite{sokolowski1992role}, and Fischer and Methfessel
  (color?)~\cite{fischer1980born}.  The latter is only plotted at
  contact, where it is defined.  }

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/pair-correlation-pretty-1.pdf}\\
  \includegraphics[width=\linewidth]{figs/pair-correlation-pretty-3.pdf}
  \caption{ \paircaption{0.1} \fixme{Do we want to label the y-axis for the 1d plots?}
  }\label{fig:pair-distribution-1}
\end{figure*}

>>>>

\newcommand\paircaption{The pair distribution function near a hard
  wall, with packing fractions of 0.1 and 0.3 and $\rr_1$ in contact with
  the hard wall.  On the left is a 2D plot of $g^{(2)}(\rr_1,\rr_2)$
  as $\rr_2$ varies.  The top half of this figure shows the result of the
  Monte Carlo simulation, while the bottom half shows the result of
  the appproximation developed in this work.  On the right is a plot
  of $g^{(2)}(\rr_1,\rr_2)$ on the path illustrated in the figure to
  the left.  This plot compares the Monte Carlo results (black) with
  those of this work (blue), Sokolowski and Fischer
  (red)~\cite{sokolowski1992role}, and Fischer and Methfessel
  (green)~\cite{fischer1980born}.  The latter is only plotted at
  contact, where it is defined.  }

@@

\begin{figure*}
  \begin{subfigure}{\textwidth}
    \includegraphics[width=\linewidth]{figs/pair-correlation-pretty-1.pdf}
    \vspace{-0.6cm}
    \caption{Pair distribution function near a hard wall with $\eta = 0.1$.}
    \label{fig:pair-distribution-1}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
    \includegraphics[width=\linewidth]{figs/pair-correlation-pretty-3.pdf}
    \vspace{-0.6cm}
    \caption{Pair distribution function near a hard wall with $\eta = 0.3$.}
    \label{fig:pair-distribution-3}
  \end{subfigure}
  \caption{ \paircaption \fixme{Do we want to label the y-axis for the 1d plots?}
  }\label{fig:pair-distribution}
\end{figure*}
